Batch Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-02-06 paper/main.tex
Paper update
First draft
Batched => Batch

% Added by wenlong lyu
\usepackage{amsmath}
\usepackage[plain]{fancyref}
\usepackage{bookmark}
\usepackage{bm}
\usepackage{todonotes}

@@

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Batched Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design}

@@

\twocolumn[
\icmltitle{Batched Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design}

@@

\input{abstract}
\input{intro}
\input{background}
\input{mace}
\input{experiments}

>>>>

% Added by wenlong lyu
\usepackage{amsmath}
\usepackage[plain]{fancyref}
\usepackage{bm}
\usepackage{todonotes}
\usepackage{placeins}

@@

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Batch Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design}

@@

\twocolumn[
\icmltitle{Batch Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design}

@@

\input{abstract}
\input{intro}
\input{background}
\input{mace}
\input{experiments}
\input{conclusion}

\FloatBarrier
